paper

### 2024-09-25 inst/extdata/paperdata/paper.qmd
.

set.seed(1234, kind = "default")

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

>>>>

set.seed(1234, kind = "default")
keep_samples <- colData(soma)$CNO != 12
soma <- soma[, keep_samples]

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)[1:6]
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled
